
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 11: Predictive Modeling - Part 2"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Install the package `mlbench` and use the follows to import the data

```{r}
library(mlbench)
data(PimaIndiansDiabetes)
df <- PimaIndiansDiabetes
```

- Set seed to be 2020. 
- The target variable is `diabetes`
- Partition the data into 80% training and 20% testing.  
```{r}
library(caret)
set.seed(2020)
splitIndex <- createDataPartition(df$diabetes, p = .80, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
```


-------

2. Tuning Decision Tree:  Use cross-validation with 10 k-folds to find the maxdepth with the greatest accuracy. Plot the accuracy associated with different maxdepths against the maxdepths. The range to search for maxdepth is from 1 to 10. 


```{r}
library(mlbench)
tuneGrid = expand.grid(maxdepth = 1:10)
trControl = trainControl(method = "cv",
number = 10)
tree_approach3 <- train(diabetes~., data=df_train,
method = "rpart2",
trControl = trControl,
tuneGrid = tuneGrid)

plot(tree_approach3)
```
```{r}
pred <- predict(tree_approach3, df_test)
cm <- confusionMatrix(data = pred, reference = df_test$diabetes, positive = "pos")
cm$overall[1]

```


-------

3. Make the final decision to select the maxdepth for your decision tree.  Is your selected maxdepth the same as the maxdepth found in 2. 

I would select the max depth of 4. This is different than maxdepth found in 2.
-------

4. Calculate the accuracy of your decision tree (the decision tree with your selected maxdepth in 3) on the test data. 

```{r}
print(tree_approach3)
```

-------

5. Redo 2-4 with an alternative method to cross-validation. 
```{r}
library(mlbench)
tuneGrid = expand.grid(maxdepth = 1:10)
trControl = trainControl(method = "LGOCV",
number = 10)
tree_approach2 <- train(diabetes~., data=df_train,
method = "rpart2",
trControl = trControl,
tuneGrid = tuneGrid)
plot(tree_approach2)
```

