
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 7: Visualization - Some aspects of ggplot2"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
library(tidyverse)
df <- read.csv('https://covidtracking.com/data/download/all-states-history.csv')
```
-------

1. Make a plot using `face_wrap` by one categorical variable 
```{r}
df %>% ggplot(mapping=aes(x=deathIncrease, y=hospitalizedIncrease)) + geom_point()+ facet_wrap(~state)
```

2. Make a plot using `face_wrap` by two categorical variables (`face_wrap(variable1~variable2)`)
```{r}
df %>% filter(state=='NH'|state=='MA') %>% ggplot(mapping=aes(x=deathIncrease), (y=hospitalizedIncrease)) + facet_wrap(date~state)
```

3. Make a plot using `position ='jitter'`. 
```{r}
df %>% filter(state=='NH'|state=='MA') %>% ggplot() + geom_point(mapping=aes(x=deathIncrease, y=hospitalizedIncrease, color=state), position='jitter')
```

4. Make a plot using `position ='dodge'`.
```{r}
df %>% filter(state=='NH'|state=='MA') %>% ggplot() + geom_point(mapping=aes(x=deathIncrease, y=hospitalizedIncrease, color=state), position='dodge')
```

5. Make a plot using `position ='fill'`. 
```{r}
df %>% filter(state=='NH'|state=='MA') %>% ggplot() + geom_point(mapping=aes(x=deathIncrease, y=hospitalizedIncrease, color=state), position='fill')
```

6. Make a plot using `geom_col`.
```{r}
df %>% filter(state=='NH'|state=='MA') %>% ggplot() + geom_col(mapping=aes(x=deathIncrease, y=hospitalizedIncrease, color=state))
```

7. Change the theme of one of your plots. 
```{r}
df %>% filter(state=='NH'|state=='MA') %>% ggplot() + geom_col(mapping=aes(x=deathIncrease, y=hospitalizedIncrease, color=state)) + theme_dark()
```

8. Save a plot and put a link of the plot to your Github Webpage.  To link a plot `abc.png` you just need to insert the following on the README.md

```{r, eval=FALSE}
[Link to the plot](abc.png)
```





