
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 8: Visualization - Making a bar race"

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Install two packages `gganimate` and `gifski` then restart Rstudio. Use the WHO's dataset at [this link](https://covid19.who.int/WHO-COVID-19-global-data.csv). Make a top-10 bar race by months between countries on the number of deaths by Covid 19.  
```{r}
library(gganimate)
library(ggplot2)
library(tidyverse)
library(knitr)


df <- read_csv('https://covid19.who.int/WHO-COVID-19-global-data.csv')
```

```{r}
df$month <- df$Date_reported
d1 <- df %>% group_by(month, Country) %>% summarise(mean=mean(Cumulative_deaths))
d2 <- d1 %>% group_by(month) %>% mutate(rank=rank(-mean)) %>% ungroup()
d3 <- d2 %>% filter(rank <= 10)
b1 <- d3 %>% ggplot(aes(x=rank, y=mean, group=Country, fill=Country, label=Country)) + geom_col()+
    geom_text(aes(y = mean, label = Country), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+
  labs(title = 'Month', x='', y='Total Number of Deaths', fill='Country')+
    theme(plot.title = element_text(hjust = 1, size = 22),
          axis.ticks.y = element_blank(),
          axis.text.y  = element_blank()) + 
    transition_states(month)+
    ease_aes("cubic-in-out")

animate(b1, nframes = 100, fps = 10)
```

2. Make another bar race using that dataset.  
```{r}
ggplot(d1, aes(x=Country, 
                 y=mean, 
                 fill=mean)) + 
  geom_col()+
  ylim(0, 25000)+
  transition_states(month)+
  labs(title = 'Mean: {closest_state}')

```

3. Make a bar race using a dataset of your own interest. You may use the dataset that we use in class (https://covidtracking.com/data/download/all-states-history.csv) but you should make a different bar racev from ones in the slides. 
```{r}
ggplot(d1, aes(x=Country, 
                 y=month, 
                 fill=mean)) + 
  geom_col()+
  ylim(0, 25000)+
  transition_states(month)+
  labs(title = 'Month: {closest_state}')
```

