
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 14: Writing a function - Loop"
---

-------

1. Write the following function. Give examples to test your function.

- Input: a data frame
```{r}
numeric_impute <- function(d)
{
  for (i in 1:length(d))
  {
      d[[i]] <- mean_impute(mean(i))
  }
  return(d)
}
```



-------

2. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: a data frame with all the missing of variables replaced by the associated means (for numeric variables) or modes (for non-numeric variables).


```{r}
numeric_impute <- function(d)
{
  for (i in 1:length(d))
  {
    if(is.numeric(d[[i]]))
    {
      d[[i]] <- mean(d[[i]],na.rm = TRUE)
    }
    else
    {
      numeric_impute <- function(d)
{
  for (i in 1:length(d))
  {
      d[[i]] <- mode_impute(d[[i]])
  }
      
  }
  return(d)
}}}
```

-------

3. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: Bar plots of all non-numeric variables

Hint: [Similar function](https://bryantstats.github.io/math421/gganimate/14_writing_functions.html#32)

```{r}
density_plot <- function(d)
{
  library(ggplot2)
  for (i in 1:length(d))
  {
    if (is.numeric(d[[i]]))
    {
      print(ggplot(d, aes(x = d[[i]]))+ 
              geom_bar()+
              labs(x = names(d)[i]))
    }
  }
}
```

-------

4. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: all possible the bar plots of a non-numeric variable filled by a non-numeric variable.

Hint: [Similar function](https://bryantstats.github.io/math421/gganimate/14_writing_functions.html#40)
```{r}
density_plot2 <- function(d)
{
  library(ggplot2)
  l <- length(d)
  for (i in 1:(l-1))
    for (j in (i+1):l)
  {
    if (is.numeric(d[[i]])& (!is.numeric(d[[j]])))
    {
      print(ggplot(d, aes(x = d[[i]], color = d[[j]]))+ 
              geom_bar()+labs(x = names(d)[i], color = names(d)[j]))
    }
      else
      {
        print(ggplot(d, aes(x = d[[i]], color = d[[j]]))+ 
              geom_bar()+labs(x = names(d)[i], color = names(d)[j]))
      }
  }
}
```

-------

5. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: 

  - all possible the bar plots of a non-numeric variable filled by a non-numeric variable.
  
  - all possible the density plots of a numeric variable colored by a non-numeric variable
  
  - all possible the scatter plots.

Hint: Combine [this function](https://bryantstats.github.io/math421/gganimate/14_writing_functions.html#36), [this function](https://bryantstats.github.io/math421/gganimate/14_writing_functions.html#39), and the function in Question 4. One way to combine is creating a new function, `quick_plot`, and call these three functions within `quic_kplot`. 

```{r}
scatter_plot <- function(d)
{
  library(ggplot2)
  l <- length(d)
  for (i in 1:(l-1))
    for (j in (i+1):l)
  {
    if (is.numeric(d[[i]])&is.numeric(d[[j]]))
    {
      print(ggplot(d, aes(x = d[[i]], y = d[[j]]))+ 
              geom_point()+
              labs(x = names(d)[i], y = names(d)[j]))
    }
      else if
      
 (is.numeric(d[[i]])& (!is.numeric(d[[j]])))
    {
      print(ggplot(d, aes(x = d[[i]], color = d[[j]]))+ 
              geom_density()+labs(x = names(d)[i], color = names(d)[j]))
    }
  }

    
     

    if (is.numeric(d[[i]])& (!is.numeric(d[[j]])))
    {
      print(ggplot(d, aes(x = d[[i]], color = d[[j]]))+ 
              geom_bar()+labs(x = names(d)[i], color = names(d)[j]))
    }
      else
      {
        print(ggplot(d, aes(x = d[[i]], color = d[[j]]))+ 
              geom_bar()+labs(x = names(d)[i], color = names(d)[j]))
      }
  }

 
```

