---
title: "Midterm Presentation"
author: "Stan Hultin"
date: "10/27/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
```{r}
library(tidyverse)
library(rpart)
library(rattle)
library(haven)
library(gganimate)
library(ggplot2)
library(knitr)
library(caret)
library(ranger)
library(caTools)
```
```{r}
df <- read_sas('C:\\Users\\student\\Documents\\Senior 1\\Stats R\\hdd0318cy (2).sas7bdat')
```

```{r}
df1 <- filter(df, yod==18)
```

```{r}
                      df1 <-  select(df1,"yod", "payfix","pay_ub92","age",  
                      "sex","raceethn","provider","moa", 
                      "yoa","mod","admtype", "asource" , 
                      "preopday" ,"los", "service" , "icu","ccu",    
                      "dispub92", "payer"  ,"drg","trandb", 
                      "randbg","randbs","orr", "anes","seq",   
                      "lab","dtest", "ther","blood","phar", 
                      "other","patcon","bwght","total","tot" ,  
                      "ecodub92","b_wt","pt_state","diag_adm","ancilar" ,
                      "campus","er_fee","er_chrg","er_mode","obs_chrg",
                      "obs_hour","psycchrg","nicu_day")
```
## Graph 1
```{r}
df %>% ggplot()+
  geom_smooth(mapping = aes(x = los, y = moa, color = raceethn))
```
## Graph 2
```{r}
df %>% ggplot()+
  geom_bar(mapping = aes(x = moa, fill = raceethn))
```
## Graph 3
```{r}
df %>% ggplot()+
  geom_bar(mapping = aes(x = mod, fill = raceethn))
```
## Graph 4
```{r}
df %>% ggplot()+
  geom_smooth(mapping = aes(x = moa, y = mod, color = raceethn))
```
## Graph 5
```{r}
df %>% ggplot()+
  geom_bar(mapping = aes(x = service, fill = sex))
```
## Graph 6
```{r}
df %>% ggplot()+
  geom_bar(mapping = aes(x = er_mode, fill = tot))
```
## Graph 7
```{r}
df %>% ggplot()+
  geom_bar(mapping = aes(x = er_mode, fill = sex))
```
## Graph 8
```{r}
df %>% ggplot()+
  geom_point(mapping = aes(x = tot, y = payer, color = sex))
```
## Graph 9
```{r}
df %>% ggplot()+
  geom_bar(mapping = aes(x = admtype, fill = tot))
```
## Graph 10
```{r}
df %>% ggplot()+
  geom_bar(mapping = aes(x = sex, fill = tot))
```
## Animation
```{r}

p1 <- ggplot(df, aes(x=er_mode, 
                 y=tot, 
                 fill=tot)) + 
  geom_col()+
  ylim(0, 2500)+
  transition_states(moa) +
labs(title = 'Total Charge by Month of Admission')
animate(p1, nframes=100, fps=20)
```

## Q6
6. Create another `target` variable (binary), decide the input variables and redo 1 to 5. 
```{r}
df1$target1 <- case_when(
  df1$age <18 ~ 'Child',
  TRUE ~ 'Adult')

df3 <- df1 %>% 
  select(target1,sex,raceethn,provider,moa,mod,admtype,campus,los) %>%
  filter(admtype != '' & raceethn != '' & sex != 9)
df3$age <- NULL
str(df3)
```

```{r}
df3$raceethn <- factor(df3$raceethn)
df3$provider <- factor(df3$provider)
df3$admtype <- factor(df3$admtype)
df3$campus <- factor(df3$campus)
df3$moa <- factor(df3$moa)
df3$mod <- factor(df3$mod)
df3$sex <- factor(df3$sex)
df3$los <- factor(df3$los)
```
## Rf Forest
```{r}
set.seed(2020)

splitIndex <- createDataPartition(df3$target1, p = .10, 
                                  list = FALSE)
df3_train<- df3[ splitIndex,]
df3_test <- df3[-splitIndex,]


tree_model3 <- rpart(target1 ~ ., data = df3_train,
                 control = rpart.control(maxdepth = 3))
barplot(tree_model3$variable.importance)
```
```{r}
tuneGrid <-  expand.grid(mtry = 2:4)
trControl <-  trainControl(method = "cv", number = 5)
forest_cv2 <- train(target1~., data=df3_train, 
                                method = "rf", 
                                trControl = trControl,
                                tuneGrid = tuneGrid)
plot(forest_cv2)
```

## Ranger Forest
```{r}
tuneGrid1 <-  expand.grid(mtry = 2:4,
                       splitrule = c('gini', 'extratrees'),
                       min.node.size = c(1:10))
trControl1 <-  trainControl(method = "cv",
                            number = 5)
forest_cv3 <- train(target1~., data=df3_train, 
                                method = "ranger", 
                                trControl = trControl1,
                                tuneGrid = tuneGrid1)
plot(forest_cv3)
```
## LogitBoost
```{r}
tuneGrid2 <-  expand.grid(nIter = 2:6)
trControl2 <-  trainControl(method = "cv",
                            number = 5)
boost_model2 <- train(target1~., data=df3_train, 
                                method = "LogitBoost", 
                                trControl = trControl2,
                                tuneGrid = tuneGrid2)
plot(boost_model2)
```
## Final Prediction
```{r}
pred1 <- predict(boost_model2,df3_test)
cm1 <- confusionMatrix(data = pred1, reference = factor(df3_test$target1), positive = "Child")
cm1$overall[1]
```