---
title: "Midterm Presentation"
author: "Stan Hultin"
date: "10/27/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
```{r}
library(tidyverse)
library(rpart)
library(rattle)
library(haven)
library(gganimate)
library(ggplot2)
library(knitr)
library(caret)
library(ranger)
library(caTools)
```
```{r}
df <- read_sas('C:\\Users\\student\\Documents\\Senior 1\\Stats R\\hdd0318cy (2).sas7bdat')
```

```{r}
df1 <- filter(df, yod==18)
```

```{r}
                      df1 <-  select(df1,"yod", "payfix","pay_ub92","age",  
                      "sex","raceethn","provider","moa", 
                      "yoa","mod","admtype", "asource" , 
                      "preopday" ,"los", "service" , "icu","ccu",    
                      "dispub92", "payer"  ,"drg","trandb", 
                      "randbg","randbs","orr", "anes","seq",   
                      "lab","dtest", "ther","blood","phar", 
                      "other","patcon","bwght","total","tot" ,  
                      "ecodub92","b_wt","pt_state","diag_adm","ancilar" ,
                      "campus","er_fee","er_chrg","er_mode","obs_chrg",
                      "obs_hour","psycchrg","nicu_day")
```

```{r}
df1$payfix <- NULL
df1$preopday <- NULL
df1$obs_hour <- NULL
df1$nicu_day <- NULL
```
```{r}
df1$target <-  case_when(df1$tot <26896.54 ~ 'low cost',
  TRUE ~ 'high cost')
```
```{r}
df2 <- df1 %>% 
  select(target,age,sex,raceethn,provider,moa,mod,admtype,campus,los)

df2$raceethn <- factor(df2$raceethn)
df2$provider <- factor(df2$provider)
df2$admtype <- factor(df2$admtype)
df2$campus <- factor(df2$campus)
df2$age <- factor(df2$age)
df2$moa <- factor(df2$moa)
df2$mod <- factor(df2$mod)
df2$sex <- factor(df2$sex)
df2$los <- factor(df2$los)

```


```{r}
set.seed(2018)
splitIndex <- createDataPartition(df2$target, p = .1, 
                                  list = FALSE)
df2_train <- df2[ splitIndex,]
df2_test <- df2[-splitIndex,]
```

```{r}
tree_model <- rpart(target ~ ., data = df2_train,
                 control = rpart.control(maxdepth = 3))
fancyRpartPlot(tree_model)
```

```{r}
tuneGrid <-  expand.grid(mtry = 2:4)
trControl <-  trainControl(method = "cv", number = 5)
forest_cv <- train(target~., data=df2_train, 
                                method = "rf", 
                                trControl = trControl,
                                tuneGrid = tuneGrid)
plot(forest_cv)
```

```{r}
tuneGrid1 <-  expand.grid(mtry = 2:4,
                       splitrule = c('gini', 'extratrees'),
                       min.node.size = c(1:10))
trControl1 <-  trainControl(method = "cv",
                            number = 5)
forest_cv1 <- train(target~., data=df2_train, 
                                method = "ranger", 
                                trControl = trControl1,
                                tuneGrid = tuneGrid1)
plot(forest_cv1)
```

```{r}
library(caTools)
tuneGrid2 <-  expand.grid(nIter = 2:6)
trControl2 <-  trainControl(method = "cv",
                            number = 5)
boost_model <- train(target~., data=df2_train, 
                                method = "LogitBoost", 
                                trControl = trControl2,
                                tuneGrid = tuneGrid2)
plot(boost_model)
```



## Q4
4. Plot the comparison of the models in 2. 
```{r}
results <- resamples(list(forest_rf = forest_cv,
                          forest_ranger = forest_cv1,
                          boost = boost_model))
bwplot(results)
```
## Q5
5. What is your final selection for the model? Test the accuracy of your final model on the test data. 
```{r}
pred <- predict(boost_model,df2_test)
cm <- confusionMatrix(data = factor(pred), reference = factor(df2_test$target), positive = "high cost")
cm$overall[1]
```
## Q6
6. Create another `target` variable (binary), decide the input variables and redo 1 to 5. 
```{r}
df1$target1 <- case_when(
  df1$age <18 ~ 'Child',
  TRUE ~ 'Adult')

df3 <- df1 %>% 
  select(target1,sex,raceethn,provider,moa,mod,admtype,campus,los) %>%
  filter(admtype != '' & raceethn != '' & sex != 9)
df3$age <- NULL
str(df3)
```

```{r}
df3$raceethn <- factor(df3$raceethn)
df3$provider <- factor(df3$provider)
df3$admtype <- factor(df3$admtype)
df3$campus <- factor(df3$campus)
df3$moa <- factor(df3$moa)
df3$mod <- factor(df3$mod)
df3$sex <- factor(df3$sex)
df3$los <- factor(df3$los)
```

```{r}
set.seed(2020)

splitIndex <- createDataPartition(df3$target1, p = .10, 
                                  list = FALSE)
df3_train<- df3[ splitIndex,]
df3_test <- df3[-splitIndex,]


tree_model3 <- rpart(target1 ~ ., data = df3_train,
                 control = rpart.control(maxdepth = 3))
barplot(tree_model3$variable.importance)
```
```{r}
tuneGrid <-  expand.grid(mtry = 2:4)
trControl <-  trainControl(method = "cv", number = 5)
forest_cv2 <- train(target1~., data=df3_train, 
                                method = "rf", 
                                trControl = trControl,
                                tuneGrid = tuneGrid)
plot(forest_cv2)
```

```{r}
tuneGrid1 <-  expand.grid(mtry = 2:4,
                       splitrule = c('gini', 'extratrees'),
                       min.node.size = c(1:10))
trControl1 <-  trainControl(method = "cv",
                            number = 5)
forest_cv3 <- train(target1~., data=df3_train, 
                                method = "ranger", 
                                trControl = trControl1,
                                tuneGrid = tuneGrid1)
plot(forest_cv3)
```

```{r}
tuneGrid2 <-  expand.grid(nIter = 2:6)
trControl2 <-  trainControl(method = "cv",
                            number = 5)
boost_model2 <- train(target1~., data=df3_train, 
                                method = "LogitBoost", 
                                trControl = trControl2,
                                tuneGrid = tuneGrid2)
plot(boost_model2)
```
```{r}
pred1 <- predict(boost_model2,df3_test)
cm1 <- confusionMatrix(data = pred1, reference = factor(df3_test$target1), positive = "Child")
cm1$overall[1]
```